---
title: "ATAC-seq"
date: "2020-01-28"
author: Jacques SERIZAY
bibliography: bibliography.bib
---

# ATAC-seq

IMPORTANT: This project has been written by Jacques SERIZAY, for the purpose of 
analysing public datasets. 

---  

Today you will be focusing on investigating the ATAC-seq data generated in 
Janes et al., 2018: "Chromatin accessibility dynamics across C. elegans 
development and ageing".


## Set up environment
```{r collapse = TRUE}
    PROJECT_PATH <- getwd()
    require(tidyverse)
    require(rtracklayer)
    require(org.Ce.eg.db)
    require(biomaRt)
```

## Load preveious work

```{r collapse = TRUE}
    load('results/Day2.RData')
```

---

## Get the ATAC-seq aging data
The data can be found [online](https://elifesciences.org/articles/37344) 
or reformatted for the purpose of the course in ./data/ATAC-seq.gff3 

### Questions: 
- Which format is the ATAC-seq.gff3 file? What does the file contain?
- Look at the cluster information: can you visualize variations of 
promoter accessibility during aging? // (boxplot)
- To be even better: look into Seqplots software... 
- In which tissue(s) are the associated genes transcribed & translated? 
(Hint: relate to yesterday's work...)

## Investigate the genes associated to varying promoters during aging

### Questions: 
- What is the function of genes going up (down) during aging? // gProfiler
- What are their counterpart in mammals? // BiomaRt
- What are the diseases associated to these genes? // DOSE package??
- Comment on the rationale of the analysis: we are looking at 
genes associated to promoters de-regulated during aging... 

---  

## SessionInfo 
```{r echo=FALSE}
    sessionInfo()
```
