---
title: "ChIP-seq"
date: "2020-01-28"
author: Jacques SERIZAY
bibliography: bibliography.bib
---

#  ChIP-seq

IMPORTANT: This project has been written by Jacques SERIZAY, for the purpose of 
analysing public datasets. 

---  

Today you will be focusing on investigating ChIP-seq data generated by 
the modENCODE consortium, to understand which TFs are regulating the 
promoters which are varying during aging


## Set up environment
```{r collapse = TRUE}
    PROJECT_PATH <- getwd()
    require(tidyverse)
    require(rtracklayer)
    require(org.Ce.eg.db)
    require(biomaRt)
```

## Load previous work

```{r collapse = TRUE}
    load('results/Day3.RData')
```

---

## Get the ChIP-seq data

### Questions: 
- What is modENCODE? 
- How to download all the data from modENCODE? 
- What useful format can be used here to easily get information on 
TF binding profiles? Is .bed format better than .bw format for 
our purpose? Why?

## Investigate the TFs associated to varying promoters during aging

### Questions: 
- How to summarize all the modENCODE data?
- Which metric should be calculated to see if a TF is enriched in a 
set of promoters? 
- How can you represent the importance of all TFs in each cluster? 
- Can you define binding motifs for the TFs enriched in some clusters? 

## Defining key TFs involved in aging? 

### Questions: 
- Is there a group of motifs functionally interacting? 
- What can you find in the literature about these factors?

---  

## SessionInfo 
```{r echo=FALSE}
    sessionInfo()
```
